---
title: "HW #6"
author: "Rob Vagnini"
date: "today"
editor: visual
format:
  html:
    embed-resources: true
execute:
  echo: true
  message: false
  warning: false
---

```{r setup}
library(tidyverse)
library(tidytext)
library(schrute)
```

# The Office

Let's continue to work with *The Office* text from the [schrute](https://cran.r-project.org/web/packages/schrute/index.html) package.

# Sentiment Analysis

### Over Time

Calculate the sentiment score (positive - negative) for each episode, and plot this variable over time.

#comment use two code chunk would be better

```{r}
sentscoreTO <- theoffice |> 
  unnest_tokens(word, text) |> 
  inner_join(sentiments, by = "word") |> 
  group_by(season, episode) |> 
  summarize(pos_score = sum(sentiment == "positive"),
            neg_score = sum(sentiment == "negative"),
            sent_score = pos_score - neg_score,
            .groups = "drop") |> 
  left_join(theoffice, by  = c("season", "episode")) |> 
  select(season, episode, sent_score, imdb_rating) |> 
  distinct() |> 
  mutate(numep = row_number(),
         season = as.factor(season))

head(sentscoreTO)

  
ggplot(sentscoreTO, aes(x = numep, y = sent_score, color = season)) + 
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Episode Number",
       y = "Sentiment Score",
       title = "Sentiment Scores Across \"The Office\" Episodes",
       color = "Season") + 
  theme(axis.title = element_text(family = "Times New Roman"),
        axis.text = element_text(family = "Times New Roman"),
        plot.title = element_text(family = "Times New Roman", hjust = 0.5),
        legend.text = element_text(family = "Times New Roman"),
        legend.title = element_text(family = "Times New Roman"))
```

### By Rating

Create a scatterplot of the `imdb_rating` versus the sentiment score (positive - negative), where the case is again an episode. Decide whether a linear model is a good fit to this relationship (optional, if you have had modeling classes, what model looks best?). Comment on what you find.

```{r}
ggplot(sentscoreTO, aes(x = imdb_rating, y = sent_score)) +
  geom_point() + 
  geom_smooth(method = "lm") +
  labs(title = "IMDB Rating vs. Sentiment Score",
       subtitle = "\"The Office\" Episodes",
       x = "IMDB Rating",
       y = "Sentiment Score") + 
  theme(plot.title = element_text(family = "Times New Roman", hjust = 0.5),
        plot.subtitle = element_text(family = "Times New Roman", face = "italic", hjust = 0.5),
        axis.text = element_text(family = "Times New Roman"),
        axis.title = element_text(family = "Times New Roman"))
```

*In general, we find that as the IMDB rating increases, the sentiment score tends to increase. This relationship is not incredibly strong and there is a possible quadratic relationship (rather than linear).*

#comment it is a great idea to add the smooth trend line

### Sentiment Negation

Identify at least a few negations that change the sentiment values based on the text. Use this to recreate the graphs above (or do this first, then create the graphs).

```{r}
# identifying reversal words
theoffice |> 
  unnest_tokens(bigram, text, "ngrams", n=2) |> 
  separate(bigram,
           into = c("word1","word2"),
           sep = "\\s+") |> 
  inner_join(sentiments, by = c("word2" = "word")) |> 
  filter(str_starts(word1,"n")) |>
  count(word1, sort = T) |> 
  head()
# add more reversal word: "hardly", "barely"
reversal_words <- c("not", "no", "never", "nor", "nothing", "neither")
```

```{r}
# identifying instances where reversal takes place
theoffice |>
  unnest_tokens(bigram, text, "ngrams", n=2) |>
  separate(bigram,
           into=c("word1","word2"),
           sep = "\\s+") |>
  inner_join(sentiments |> rename(sentiment0 = sentiment),
             by = c("word2" = "word")) |>
  mutate(
    sentiment = 
      case_when(
        (word1 %in% reversal_words) & sentiment0 == "positive" ~ "negative",
        (word1 %in% reversal_words) & sentiment0 == "negative" ~ "positive",
        T ~ sentiment0)
  ) |>
  filter(sentiment0 != sentiment) |> 
  select(word1, word2, sentiment0, sentiment) |> 
  head()
```

```{r}
# adjusting dataset to account for reversal words
sentscoreTOrev <- theoffice |>
  unnest_tokens(bigram, text, "ngrams", n=2) |>
  separate(bigram,
           into=c("word1","word2"),
           sep = "\\s+") |>
  inner_join(sentiments |> rename(sentiment0 = sentiment),
             by = c("word2" = "word")) |>
  mutate(
    sentiment = 
      case_when(
        (word1 %in% reversal_words) & sentiment0 == "positive" ~ "negative",
        (word1 %in% reversal_words) & sentiment0 == "negative" ~ "positive",
        T ~ sentiment0)
  ) |> 
  group_by(season, episode) |> 
  summarize(pos_score = sum(sentiment == "positive"),
            neg_score = sum(sentiment == "negative"),
            sent_score = pos_score - neg_score,
            .groups = "drop") |> 
  left_join(theoffice, by = c("season", "episode")) |> 
  select(season, episode, sent_score, imdb_rating) |> 
  distinct() |> 
  mutate(numep = row_number(),
         season = as.factor(season))

sentscoreTOrev |> 
  head()
```

```{r}
# sentiment analysis (over time)
ggplot(sentscoreTOrev, aes(x = numep, y = sent_score, color = season)) + 
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Episode Number",
       y = "Sentiment Score",
       title = "Sentiment Scores Across \"The Office\" Episodes",
       subtitle = "With Reversal Words Considered",
       color = "Season") + 
  theme(axis.title = element_text(family = "Times New Roman"),
        axis.text = element_text(family = "Times New Roman"),
        plot.title = element_text(family = "Times New Roman", hjust = 0.5),
        plot.subtitle = element_text(family = "Times New Roman", hjust = 0.5, face = "italic"),
        legend.text = element_text(family = "Times New Roman"),
        legend.title = element_text(family = "Times New Roman"))
```

```{r}
# sentiment analysis (by imdb)
ggplot(sentscoreTOrev, aes(x = imdb_rating, y = sent_score)) +
  geom_point() + 
  geom_smooth(method = "lm") +
  labs(title = "IMDB Rating vs. Sentiment Score",
       subtitle = "\"The Office\" Episodes with Reversal Words",
       x = "IMDB Rating",
       y = "Sentiment Score") + 
  theme(plot.title = element_text(family = "Times New Roman", hjust = 0.5),
        plot.subtitle = element_text(family = "Times New Roman", face = "italic", hjust = 0.5),
        axis.text = element_text(family = "Times New Roman"),
        axis.title = element_text(family = "Times New Roman"))
```

#comment great job!
